%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}%\setmainfont{Times New Roman}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage[T1]{fontenc}
% \usepackage[T1]{fontenc}
% \usepackage{cochineal}
% \usepackage{fourier}

% \usepackage{fontspec}
% \usepackage{polyglossia}
% \setmainlanguage{german}
% \setmainfont{Times New Roman}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSingleSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------\usepackage{fontspec}
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------


\begin{center}
    {\huge Maanit Malhan} \\ \vspace{2pt} 
    \small{-}
    \href{mailto:[maanitmalhan@gmail.com]}{\color{blue}{maanitmalhan@gmail.com}} ~ 
    \small{-}
    \href{[https://www.linkedin.com/in/maanit-malhan/]}{ \color{blue}{https://www.linkedin.com/in/maanit-malhan}}  ~
    \small{-}
    \href{[Maanit Malhan]}{ \color{blue}{https://github.com/maanitmalhan}} ~
    \vspace{-7pt}
\end{center}

%-----------EDUCATION-----------
\section{\color{airforceblue}EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Connecticut}{Storrs, CT, USA}
      {B.S in Computer Science, Concentration in AI/Computational Data Analytics}{December 2025(Expected)}
       \resumeItemListStart
            \resumeItem{\normalsize{Coursework includes CPU Architecture and Assembly Language, Statistics, Object-Oriented Programming I and II, Cybersecurity, Data Structures and Algorithms, Algorithms and Complexity, and Discrete Math}}
            
      \resumeItemListEnd  
    \vspace{-4pt}
     
  \resumeSubHeadingListEnd
  \vspace{-10pt}

%-----------PROGRAMMING SKILLS-----------
\section{\color{airforceblue}TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{\normalsize{Programming Languages:}}{ \normalsize{Python, C, C++, Java, HTML/CSS, JavaScript, Bash, Object-Oriented programming}} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Libraries and Tools:}}{ \normalsize{ReactJS, Plotly, Pandas, Numpy, OpenCV, YOLOv8, Git/Github, ZSH, PowerShell, Linux/Unix, WordPress, Microsoft Office Suite, Power Bi, LaTeX}} \\
      \vspace{1.2pt}
      
     
     % copy and paste above textbf block to add more 
     }}
 \end{itemize}
 \vspace{-16pt}
 
 %-----------EXPERIENCE-----------
\section{\color{airforceblue}WORK EXPERIENCE}
  \resumeSubHeadingListStart
 
 \resumeSubheading
      {FROST Robotics}{} 
      {Financial Officer/Team member}{January 2024 - Present}
      \resumeItemListStart
            \resumeItem{\normalsize{Developing a state-of-the-art Full-Body Spinning Combat Robot, gaining expertise in electronics, design, and overall functionality implementation using C and C++.}}
            \resumeItem{\normalsize{Helping fundraise by networking with companies and individuals and allocating funds as required for team projects.}}  
      \resumeItemListEnd 
      
    \resumeSubheading
      {Department of Energy, Southern New England Industrial Assessment Center}{} 
      {Software developer/Student assessor}{September 2023 - Present}
      \resumeItemListStart
            \resumeItem{\normalsize{Used HTML and CSS to create pages on and manage our website, iac.uconn.edu}}
            \resumeItem{\normalsize{Invented powerful software using Python to effortlessly retrieve, manipulate, and visualize database data, automating value extraction, document presentation, and calculations.}} 
            \resumeItem{\normalsize{Developing a full-stack web application featuring auto-fill functionality, dynamically populating fields based on previously entered data associated with specific codes.}}  
      \resumeItemListEnd  

    \resumeSubheading
      {University of Connecticut FSAE}{} 
      {Team member(Data acquisition sub-team)}{August 2023 - Present}
      \resumeItemListStart
            \resumeItem{\normalsize{Prepare, organize, and facilitate track and test days.}}
            \resumeItem{\normalsize{As a UConn FSAE Data Acquisition (DAQ) team member, I set up telemetry sensors using electrical skills and then analyzed and graphed useful recorded data using Python.}}  
      \resumeItemListEnd  



    \resumeSubheading
      {University High School of Science and Engineering}{} 
      {Teaching Assistant}{August 2022 - June 2023}
      \resumeItemListStart
            \resumeItem{\normalsize{Instructed a class of 25 students in PLTW Principles of Engineering.}}
            \resumeItem{\normalsize{Taught students the applications of robotics, simple machines, compound machines, circuits, and programming.}}  
            \resumeItem{\normalsize{Offered one-on-one and small-group student assistance during class, addressing questions and clarifying concepts.}}  \resumeItemListEnd  
      
   \resumeSubheading
      {FIRST Robotics Team - Team 1991}{} 
      {Captain and Sub-team Lead}{August 2019 - June 2023}
      \resumeItemListStart
            \resumeItem{\normalsize{Led a team of 50 Students split between Corporate, Mechanical, Design, Programming and Electrical Sub-teams.}}
            \resumeItem{\normalsize{Programmed all aspects of the robot using Java.}}  
      \resumeItemListEnd  

    \resumeSubheading
      {FIRST Lego League - Team 55523 }{} 
      {Lead Student Mentor}{August 2022 - May 2023}
      \resumeItemListStart
            \resumeItem{\normalsize{Volunteered to Mentor eight members in programming LEGO robots to complete missions on the competition field, teaching basic coding principles and best practices in programming.}}
      \resumeItemListEnd  
    % copy and paste above resumeSubheading block to add more 
  \resumeSubHeadingListEnd
\vspace{-12pt}


 %-----------PROJECTS-----------
\section{\color{airforceblue}PROJECTS}    
    \resumeItemListStart
        \vspace{0.5pt}

        \resumeItem{\normalsize{\textbf{T.A.L.L language-learning}, Under development is a demo—ready software that uses AI to help students learn languages. Students trace letters or words on a canvas, and the work is checked using AI.
        Helps students improve vocabulary,  letter recognition, and motor skill development.}}
        \vspace{-5pt}

        \resumeItem{\normalsize{\textbf{RoboSight}, Initially developed as a demonstration of vision software. Updated to integrate the vision software with the robot’s hardware devices and sensors for real-world scenarios like auto-aim/auto-shooting and object tracking with more accuracy and control than the default software.}}  
        \vspace{-5pt}


        % copy and paste above resumeItem block to add more 
        
    \resumeItemListEnd  
   
 \vspace{-12pt}

\end{document}
